---
title: "R Notebook"
output: html_notebook
---

Let's look at network graphs

```{r}
# install.packages("igraph")

## Load packages
require("igraph")

g3 <- graph( edges=c("cheese","Pizza", "cheese","hamburger", "cheese","fries", "Pizza","pepperoni", "Pizza","hamburger"), directed = F)

plot(g3) # A simple plot of the network - we'll talk more about plots later
```


```{r}
require("igraph")


g3 <- graph( edges=c(c("cheese","fries"),c("cheese","pizza"),c("cheese","burger")), directed = F)
plot(g3)
```


connect to the DB
```{r}
# install.packages("RPostgreSQL")
# install.packages("compare")
require("RPostgreSQL")
require("compare")

# Load the PostgreSQL driver, create a connection to the postgres database
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "mycodb", host = "localhost", port = 5432, user = "ruser", password = "ruser")
sql_string <- paste("SELECT * FROM mycodb", sep="")
MycoDB <- data.frame(dbGetQuery(con, sql_string))
```

Let's make a sample and then see what arbitrary connections look like
```{r}
print("Plants**************************************************")
plantsample<-sample(unique(MycoDB$plantfamily), size = 10)
plantsample

print("Fungi**************************************************")
fungisample<-sample(unique(MycoDB$fungalgenus), size = 10)
fungisample
```
Now let's hand code some examples?
```{r}
require("igraph")

g3 <- graph( edges=c(c("hydnum","apiaceae",
                       "hydnum","cyperaceae", 
                       "hydnum","urticaceae", 
                       "hydnum","liliaceae"),
                     c("gummiglobus","cyperaceae"),
                     "gummiglobus","arecaceae",
                     "gummiglobus","erythroxylaceae",
                     "gummiglobus","anacardiaceae"), directed = F)
plot(g3)
```

One more 'gin
```{r}
print("Plants**************************************************")
plantsample<-sample(unique(MycoDB$plantfamily), size = 20)
plantsample

print("Fungi**************************************************")
fungisample<-sample(unique(MycoDB$fungalgenus), size = 10)
fungisample
```


```{r}
require("igraph")

g3 <- graph( edges=c(c("russula","apiaceae",
                       "russula","cyperaceae", 
                       "russula","urticaceae", 
                       "russula","liliaceae"),
                       c("hebeloma","apiaceae",
                       "hebeloma","cyperaceae", 
                       "hebeloma","urticaceae", 
                       "hebeloma","arecaceae"),
                     c("gummiglobus","cyperaceae"),
                     "gummiglobus","arecaceae",
                     "gummiglobus","erythroxylaceae",
                     "gummiglobus","anacardiaceae"), directed = F)
plot(g3)
```

Let's try and take an IRL cut
```{r}
# g3 <- graph(edges=c(unique(subset(MycoDB$fungalgenus, MycoDB$fungalgenus != NA)), MycoDB$plantfamily), directed = F)
# FileDirectory <- paste("/home/daiten/Programming/R/Projects/MycoDB/Graphics/", sep="")
# png(paste(FileDirectory, "FungiFamilyLarge.jpg", sep = ""), width = 10000, height = 10000)
# plot(g3)
# dev.off
```

So that's an unholy mess. Let's take a sample and try.
```{r}
# sampleset <- sample(MycoDB, size = 1000, replace = TRUE)
# sampleset

fungisubset <- subset(MycoDB, ! is.na(MycoDB$fungalgenus))

fungivector <- fungisubset[,'fungalgenus']
plantvector <- fungisubset[,'plantfamily']

g3 <- graph(edge = c(fungivector, plantvector), directed = F)
FileDirectory <- paste("/home/daiten/Programming/R/Projects/MycoDB/Graphics/", sep="")
png(paste(FileDirectory, "FungiFamilyLarge.jpg", sep = ""), width = 5000, height = 5000)
plot(g3, vertex.size=1)
dev.off()

```

That's it but it looks wrong....Let's try one more time....
```{r}
fungalsubset <- subset(MycoDB, ! is.na(MycoDB$fungalgenus))
rhizoglomus <- subset(fungalsubset, fungalsubset$fungalgenus == "rhizoglomus")
networkmap <- graph(edge = c(rhizoglomus$fungalgenus, rhizoglomus$plantfamily))
FileDirectory <- paste("/home/daiten/Programming/R/Projects/MycoDB/Graphics/", sep="")
png(paste(FileDirectory, "rhizoglomus.jpg", sep = ""), width = 5000, height = 5000)
plot(networkmap, vertex.size=1)
dev.off()
```

Still not right.
Some how we ned to create this structure
g3 <- graph( edges=c(c("hydnum","apiaceae",
                       "hydnum","cyperaceae", 
                       "hydnum","urticaceae", 
                       "hydnum","liliaceae"),
                     c("gummiglobus","cyperaceae"),
                     "gummiglobus","arecaceae",
                     "gummiglobus","erythroxylaceae",
                     "gummiglobus","anacardiaceae"), directed = F)
                     
And have it work through....

